Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-07-30 sections/results.tex
fix numbers in table
revise RQ1 result

\subsubsection{Removal of automatically generated messages} To consider only reviewers discussion, we ignored all messages that automatically generated.
%In Gerrit, the comment history is composed of human-written comments from reviewers and automatically generated messages.
These automatic messages are generated by Gerrit, continuous integration system, and the sanity bot\footnote{It is a bot that automatically checks new proposed changes for trivial sanity issues, such as line endings, copyright notices, and commit messages} to record activities. \textit{`Upload patch set 1.'}, \textit{`Change has been successfully cherry-picked to the staging branch as ...'}, and \textit{`Sanity review passed'} are some examples. In practice, they are not considered in code review  and are not substantially relevant to the proposed changes and do not directly impact software quality\cite{Mcintosh}.

To do so, we first ignore all comments written by bots (i.e. \emph{Qt Continuous Integration System} and \emph{Qt Sanity Bot}). Second, we removed message including reviewers comments by finding common patterns frequently occurred using regular expression. This would leave us only human-written comments that will be used in further preprocessing.

@@

\subsection{Manual Comment Usefulness Assessment}
In this case study, three participants (the first two authors and one student) independently classified comments by giving a question, ``does this comment technically contribute to its change or not?''
Then, the participants gave a vote for \texttt{YES} if the comment is likely to be useful and \texttt{NO} otherwise.
From the voting scores, we regarded that the comments with three \texttt{YES} votes are \emph{useful} comments and the comments with no \texttt{YES} votes (i.e. three \texttt{NO} votes) are \emph{useless} comments. For the comments with one and two \texttt{YES} votes, we defined them as unclear comments.

@@

\begin{figure}[!t]
\centering
\includegraphics[scale=0.45, trim=0 0 30 50, clip=true]{scatter_log}
\caption{The similarity and distance plot of the training data.
The symbol represents the score, which ranges from 0 to 3.
The green area represents the \emph{useful} classification model and the red area represents the \emph{useless} model.}
\label{fig:scatter}
\end{figure}

@@

To determine similarity and dissimilarity thresholds for useful and useless model, we iterated $s_t$ and $d_t$ values from every unique similarity and dissimilarity values in our data set.
%Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F$_1$ score.
We selected the thresholds that best classify useful and useless comments based on F-measure score and applied models.
The selected models are $\Theta(c,S_T=0.015529,D_T=2.494944)$ for useful comments, and $\Omega(c,S'_T=0.087522,D'_T=2.265679)$ for useless comments.

\textbf{Model Effectiveness Results:} From 318 samples, the number of labeled comments were 85, 60, 51, and 122 for 0, 1, 2, and 3 \texttt{YES} votes, respectively.
The precision and recall of the models are 0.701 and 0.787 for useful model, and 0.648 and 0.824 for useless model.
We summarized the number of comments by manually-classified score and our classification result in Table \ref{tb:classify_number}.
The results and relationship between manual classification and our model based on similarity thresholds are shown in Fig  \ref{fig:scatter}.
Comments in the green area are those that satisfied the conditions of the useful model.
Comments in the red area are those that satisfied condition of the useless model.
Finally, comments in the white area are those that did not satisfy any condition (i.e. \emph{undetermined}). 
%This figure also shows an example comment that fall in the different area\pick{Didn't put yet}.

%%Interpret: comments & model%%%%
As shown in the figure, most useful comments went into the green area; only few useful comments ended up in the red area.
Similarly, most useless comments went into the red area.
The unclear comments are drawn in both area.
Between these areas, there is an overlap section.
This is because the similarity and dissimilarity values between useful and useless are vague.
Both models tried to maximize the coverage (and the precision) of classification, which makes it possible that there is some overlapping between these two models.
Fortunately, this overlapping area is small.

% These should go into the discussion.
%However, from the results in Table \ref{tb:classify_number}, only three comments were classified in the overlapping section.
%This shows that error of our models is low. Furthermore, there are 12 useless comments  (14\%) and 21 useful comments (17\%) still are undetermined (drawn in white area). We investigate characteristics of these comments. The findings are described in our discussion section.
%From the example comment, it shows that these comments discussed on \TODO{insert topic}, but did not contain any word in common.

\begin{table}[!t]
\centering
\small
\caption{Number of comments classified by our approach against ground truth data}
\begin{tabular}{ccccc}
\hline
& \multicolumn{4}{c}{Class from Manual Assessment} \\ \cline{2-5}
Our&  Useless  & Unclear  & Unclear & Useful \\
Classifications&  (\texttt{YES}=0) & (\texttt{YES}=1) & (\texttt{YES}=2) & (\texttt{YES}=3) \\
\hline \hline
Useful & 3 & 12 & 24 & 94 \\
Useless & 69 & 23 & 7 & 6 \\
Overlap & 1 & 1 & 0 & 1 \\
Undetermined & 12 & 24 & 20 & 21 \\
\hline
\end{tabular}
\label{tb:classify_number}
\end{table}

%%Interpret: comments & similarity values%%%%
The graph also shows that the useful comments have low dissimilarity value (less than 3, approximately),
while most useless comments have zero similarity.
However, the unclear comments are spread out over the graph in a way which we cannot classify using our model.
This suggests that other factors may come into play.

%Interestingly, comments can be clearly separated into two major groups: comments with high similarity values and comment with zero similarity. This indicates that the comments  in each group have relationship other than similarity. This led us to investigate insight into these comments to find other properties in our future work.

Interestingly, in Table \ref{tb:classify_number},
89\% of useful-class comments received 2 or 3 \texttt{YES} votes,
and 88\% of useless-class comments received 0 or 1 \texttt{YES} votes.

%Probably should be in the discussion?
% As manual classification can be subjective, these comments were not received three voting scores.
% It is possible that the unclear comments with \texttt{YES} = 2 can be useful comments and comments with can be useless comments.

@@

\textbf{Validation:}
We validated our approach using bootstrapping cross validation.
We randomly selected 90\% of 318 comments for training set and determine thresholds.
The constructed model is then applied on the remaining 10\% comments as the validation set.
The precision, recall and F-measure scores are measured and recorded.
This validation was repeated 300 times to give an average performance of our models.
For a baseline, we also determined the performance of the random classifier using the same methods.

Table \ref{tb:xvalidate} describes the performance of useful and useless classification models including an average and standard deviation of precision, recall, and F-measure.
The results show that both of our models can achieve 60\% of precision and 75\% of recall, approximately.
In addition, our models also achieved higher results than the random models twice for both precision and recall.

@@

According to the results, we can answer RQ1 that \emph{there is a relation between semantic similarity usefulness of comments. Based on our approach, the semantic similarity can be used as an indicator to classify usefulness of comments. }

@@

To answer this question, timestamps are recorded as three people voted on each comment.
Since three people work in their leisure time, there is much variability in the time between each vote.
Therefore, we ignored the time interval between two votes if they are more than 10 minutes apart.

@@

Applying our classification model to all comments results in the proportions shown in Table \ref{tb:percent}.
As the table shows, the proportions are very similar in both the training dataset and all dataset,
which may suggest that our model will have a similar performance in the real data.

\begin{table}[!t]
\caption{Proportion of classifications when applied to the whole data set.}
\small
\centering
\def\arraystretch{1.2}
\begin{tabular}{ccccccc}
\hline
Classification & over all samples & only training data  \\ \hline
useful &            42.8\%      &      41.8\%         \\
useless &           33.7\%      &      33.1\%         \\
undetermined &      23.5\%      &      25.1\%         \\ \hline
\end{tabular}
\label{tb:percent}
\end{table}

>>>>

\subsubsection{Removal of automatically generated messages} To consider only reviewers discussion, we ignored all messages that automatically generated.
%In Gerrit, the comment history is composed of human-written comments from reviewers and automatically generated messages.
These automatic messages are generated by Gerrit, continuous integration system, and the sanity bot\footnote{It is a bot that automatically checks new proposed changes for trivial sanity issues, such as line endings, copyright notices, and commit messages} to record activities. For example, \textit{`Upload patch set 1.'}, \textit{`Change has been successfully cherry-picked to the staging branch as ...'}, and \textit{`Sanity review passed'}. In practice, they are not considered in code review  and are not substantially relevant to the proposed changes and do not directly impact software quality\cite{Mcintosh}.

To do so, we first ignore all comments written by bots i.e. \emph{Qt Continuous Integration System} and \emph{Qt Sanity Bot}. Second, we removed message including reviewers comments by finding common patterns frequently occurred using regular expression. This would leave us only human-written comments that will be used in further preprocessing.

@@

\subsection{Manual Comment Usefulness Assessment}
In this case study, three participants (the first two authors and one student) independently classify comments by giving a question, ``does this comment technically contribute to its change or not?''
Then, the participants gave a vote for \texttt{YES} if the comment is likely to be useful and \texttt{NO} otherwise.
From the voting scores, we regarded that the comments with three \texttt{YES} votes are \emph{useful} comments and the comments with no \texttt{YES} votes (i.e. three \texttt{NO} votes) are \emph{useless} comments. For the comments with one and two \texttt{YES} votes, we defined them as unclear comments.

@@

\begin{figure}[!t]
\centering
\includegraphics[scale=0.45, trim=0 0 30 50, clip=true]{scatter_log}
\caption{The similarity and distance plot of the training data.
The symbol represents the score, which ranges from 0 to 3.}
\label{fig:scatter}
\end{figure}

@@

To determine similarity and dissimilarity thresholds for useful and useless model, we iterated $s_t$ and $d_t$ values from every unique similarity and dissimilarity values in our data set.
%Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F$_1$ score.
We selected the thresholds that best classify useful and useless comments based on F-measure score and applied models, i.e. useful: $\Theta(c,S_T=0.015529,D_T=2.494944)$ and useless: $\Omega(c,S_T=0.087522,D_T=2.265679)$ on the samples.

\textbf{Model Effectiveness Results:} From 318 samples, the comment sets from manual assessment were 85, 60, 51, and 122 for useless set (\texttt{YES} = 0), unclear set (\texttt{YES} = 1 or 2), and useful set (\texttt{YES} = 3), respectively. The precision and Recall of the models were 0.701 and 0.787 for useful model and 0.648 and 0.824 for useless model.

Figure \ref{fig:scatter} shows the relationship between usefulness class from our classification model and comment sets from manual assessment. 
The green area represents the \emph{useful} classification model and the red area represents the \emph{useless} classification model. The comments drawn in the green area are those satisfied condition of useful model and the comments drawn in the red area are those satisfied condition of useless. While, the comments drawn in the white area are those not satisfied any condition (i.e. \emph{undetermined}). 
The total number of comments from this classification results is described in Table \ref{tb:classify_number}.

%%Interpret: comments & model%%%%
Corresponding to the precision and recall values, the figure shows that most comments drawn in green area are comments of useful set and very few comments of useless set drawn in this area. Similarly, most comments in the red area are comments of useless set. It also shows that the similarity and dissimilarity values of comments in each set are not different from other comments in the same set. Most of useful set (\texttt{YES} = 3) adhere in the top left of the graph while useless set (\texttt{YES} = 0) adhere in the bottom right of the graph. However, the unclear set still spread out over the graph which we cannot determine relationship between their similarity values.

There is an overlap section as shown in Fig. \ref{fig:scatter}. This is a conflict results between our two models where a comment received true outcome from both classification models.  
This is phenomenon can occur since similarity and dissimilarity values of each group are vague and both  models tend to maximize coverage of classification. However, from the results in Table \ref{tb:classify_number}, only three comments were selected by both models (overlap). This is very small error for our models. Excluding the overlap classification result, we can calculate precision and recall as described in Table \ref{tb:classify_number}. Furthermore, there are 12 useless comments (14\%) and 21 useful comments (17\%) still are undetermined (drawn in white area). These comments were not satisfied our models. This suggests us that other indicators are needed to satisfy condition and identify usefulness.
%From the example comment, it shows that these comments discussed on \TODO{insert topic}, but did not contain any word in common.

\begin{table}[!t]
\centering

\caption{Number of comments classified by our approach against ground truth data}
\begin{tabular}{cccccc}
\hline
Result from & \multicolumn{4}{c}{Results from manual assessment}  & \multirow{3}{*}{Precision}\\ \cline{2-5}
Classification &  Useless  & Unclear  & Unclear & Useful \\
Models&  (\texttt{YES}=0) & (\texttt{YES}=1) & (\texttt{YES}=2) & (\texttt{YES}=3) \\
\hline \hline
Useful & 3 & 12 & 24 & 94 & 0.706\\
Useless & 69 & 23 & 7 & 6 &  0.657\\
Overlap & 1 & 1 & 0 & 1 & - \\
Undetermined & 12 & 24 & 20 & 21 & - \\
\hline
Recall & 0.812 & - & - & 0.770\\ \hline 
\end{tabular}
\label{tb:classify_number}
\end{table}

@@

\textbf{Validation:} We validated our approach using bootstrapping cross validation. We randomly selected 90\% of 318 comments for training set and determine thresholds. We then applied the constructed model on the remaining 10\% comments as the validation set.
The performance on the validation sets was measured using precision, recall and F-measure.
This validation was repeated for 300 times to estimate the performance of our models.
For a baseline of our models, we determined the performance of the random models using same methods.

Table \ref{tb:xvalidate} describes the performance of useful and useless classification models including an average and standard deviation of precision, recall, and F-measure. The results show that both of our models can achieve  60\% of precision and  75\% of recall approximately. Moreover, our models also achieved higher results than the random models twice for both precision and recall.

@@

According to the results, we can answer RQ1 that \emph{using semantic similarity values as indicators, our approach successfully classify comment usefulness with precision of 0.6 and recall of 0.7 approximately and this is better than random model as twice.}

@@

To answer this question, timestamps are recorded as three people assess each comment.
Since three people work on their leisure time, there is much variability in the time between each vote.
Therefore, we ignored the time interval between two votes if they are more than 10 minutes apart.

@@

Applying our classification model to all comments results in the proportions shown in Table \ref{tb:percent}.
As the figure shows, the proportion is similar to the result of .

\begin{table}[!t]
\caption{Proportion of classifications when applied to the whole data set.}
\small
\centering
\def\arraystretch{1.2}
\begin{tabular}{ccccccc}
\hline
Class &        over all samples & only training data  \\ \hline
useful &            42.8\%      &      41.8\%         \\
useless &           33.7\%      &      33.1\%         \\
undetermined &      23.5\%      &      25.1\%         \\ \hline
\end{tabular}
\label{tb:percent}
\end{table}
